\documentclass[a4paper,12pt]{article}


\usepackage{amssymb}
\usepackage[margin=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{amsmath}

 
\pagestyle{fancy}
\fancyhf{}
\lfoot{Monday 9-11 Group I}
 

\begin{document}

\section{User Stories}


\textbf{Epic: As a user, I want a cryptogram game so that I can solve cryptogram puzzles and then be scored on my performance.}


\begin{itemize}

  \item As a player of the game, I want the ability to have an individual account within the app so that I can keep track of my own progress and compete on the leader board against other players.

  \item As a player of the game, I want the ability to be prompted with a hint that will fill in a correct letter within the puzzle. There should be no limit on the amount of times that I can use this feature and it should not impact my score.

  \item As a player of the game, I want the ability to give up and be shown the correct solution to the puzzle if I find it too hard. 

  \item As a player of the game, I want the ability to save a games progress so that I can continue it at a later stage. 

  \item As a player of the game, I want to be prompted with an error if I have already mapped my input to a letter in the puzzle.

  \item As a player of the game, I want to be able to see the frequency that different letters appear within the puzzle so that I can solve the puzzle a little bit easier. 

  \item As a player of the game, I want ability to quickly log back into my individual account without having to authenticate my identity. 

  \item As a player of the game, I want the game to track my total number of cryptograms played, number of games won, best games (correct guesses divided by total guess in a single guess)

  \item As a player of the game, I want to able to view the leader board so I can see how all my friends are playing so that I can try and beat them!

  \item As a player of the game, I want the ability to sort the leader board to view different statistics (for example the top ten most successful or unsuccessful players who have played the game) 

\end{itemize}





\end{document}

